---
title: "Main Models and Diagnostics Plots"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          code_folding: hide
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this document, I will show our main models and their respective diagnostics
plots. The full explanation about these analyses can be found in our preregistered
analysis plan: [https://osf.io/kvuqr/](https://osf.io/kvuqr/)

In case you are interested in the R code, you can click in the "Code" → 
"Show All Code" option in the right upper corner of this document.

```{r}
pacman::p_load(tidyverse, # Data wrangling
               brms, # to fit Bayesian models
               tidybayes, # to wrangle and plot brms data
               rio, # to import/export files
               here, # reproducible file paths
               metafor) # to calculate log OR

# Load function to plot diagnostics

source(here("final_analyses/functions/diag_plot.R"))

set.seed(123)
```

```{r}
# Load original data file
d = import(here("final_analyses", "data", "mortality_data.xlsx"))

# Remove studies that have 0 total events in both treatment arms (3 studies)
d = 
  d %>% 
  filter((control_events + trt_events) != 0)

# Calculate log odds ratio

d_logOR = 
  escalc(
  measure = "OR", # log odds ratio,
  
  # Tocilizumab/Sarilumab
  ai = trt_events,
  n1i = trt_total,
  
  # Control
  ci = control_events,
  n2i = control_total,
  
  data = d
) %>%
  as_tibble() %>% 
  # Dummy approach, tocilizumab = 0, sarilumab = 1
  mutate(treatment = ifelse(treatment == "tocilizumab", 0, 1)) %>% 
  # Calculate standard error
  mutate(sei = sqrt(vi)) 
```

# Sarilumab only model

### Model

$$
\begin{align*}
y_i & \sim Normal(\theta_i, \sigma_i^2) \tag{Likelihood}\\
\theta_i & \sim Normal(\mu_{sarilumab}, \tau^2)\\
\\
\mu_{sarilumab} & \sim \operatorname{Normal}(0, 1.5^2) \tag{Priors}\\
\tau & \sim \operatorname{Half-Normal}(0.5) \\
\end{align*}
$$


```{r, results="hide"}
## Formula
mf = 
  # https://bookdown.org/content/3890/horoscopes-insights.html#use-the-0-intercept-syntax
  formula(yi | se(sei) ~ 0 + Intercept + (1 | study))

## Priors
priors = 
  prior(normal(0, 1.5), class = "b", coef = "Intercept") + 
  prior(normal(0, 0.5), class = "sd") # Half-Normal(0.5)

## Fit model (suppressed)

# model_sarilumab_only = 
#   brm(
#   data = d_logOR %>% filter(treatment == "1"), # only sarilumab
#   family = gaussian,
#   
#   formula = mf,
#   prior = priors,
#   sample_prior = TRUE,
#   
#   
#   backend = "cmdstanr", # faster
#   cores = parallel::detectCores(),
#   chains = 4,
#   warmup = 2000,
#   iter = 4000,
#   control = list(adapt_delta = .95),
#   seed = 123,
#   
#   file = here("final_analyses/output/fits/main/model_sarilumab_only")
# )

# Load model
model_sarilumab_only = 
  readRDS(here("final_analyses/output/fits/main/model_sarilumab_only.rds"))
```

```{r}
print(model_sarilumab_only)
```

### Diagnostics plots

```{r, fig.align='center'}
diag_plot(model = model_sarilumab_only,
          pars_list = c("b_Intercept", "sd_study__Intercept"),
          ncol_trace = 4)
```
Posterior predictive check

```{r, fig.align='center'}
pp_check(model_sarilumab_only, nsamples = 50)
```

# Sarilumab vs. Tocilizumab model

### Model

$$
\begin{align*}
y_i & \sim Normal(\theta_i, \sigma_i^2) \tag{Likelihood} \\
\theta_i & \sim Normal(\mu, \tau^2)\\
\mu &= \beta_0 + \beta_1 x\\
\\
\beta_0 & \sim \operatorname{Normal}(0, 1.5^2) \tag{Priors} \\
\beta_1  & \sim \operatorname{Normal}(0, 1^2) \\
\tau & \sim \operatorname{Half-Normal}(0.5) \\
\end{align*}
$$

```{r, results="hide"}

# Formula
mf = 
  formula(yi | se(sei) ~ 0 + Intercept + treatment + (1 | study))

priors = 
  prior(normal(0, 1.5), class = "b", coef = "Intercept") +
  prior(normal(0, 1), class = "b", coef = "treatment") +
  prior(normal(0, 0.5), class = "sd") 


# model_sarilumab_vs_tocilizumab =
#   brm(
#   data = d_logOR,
#   family = gaussian,
#   
#   formula = mf,
#   prior = priors,
#   sample_prior = TRUE,
#   
#   
#   backend = "cmdstanr", # faster
#   cores = parallel::detectCores(),
#   chains = 4,
#   warmup = 2000,
#   iter = 4000,
#   control = list(adapt_delta = .95),
#   seed = 123,
#   
#   file = here("final_analyses/output/fits/main/model_sarilumab_vs_tocilizumab")
# )

model_sarilumab_vs_tocilizumab =
  readRDS(here("final_analyses/output/fits/main/model_sarilumab_vs_tocilizumab.rds"))

```

```{r}
print(model_sarilumab_vs_tocilizumab)
```

### Diagnostics plots

```{r, fig.align='center'}
diag_plot(model = model_sarilumab_vs_tocilizumab,
          pars_list = c("b_Intercept", "b_treatment", "sd_study__Intercept"),
          ncol_trace = 4)
```
Posterior predictive check

```{r, fig.align='center'}
pp_check(model_sarilumab_vs_tocilizumab, nsamples = 50)
```

# Sarilumab + Tocilizumab as prior model

## Tocilizumab only model

$$
 \begin{equation*}
    \sigma_{i[W]}^2 =  \frac{1}{Wa_i+\frac{1}{2}} +
    \frac{1}{Wb_i+\frac{1}{2}} +
    \frac{1}{Wc_i+\frac{1}{2}} +
    \frac{1}{Wd_i+\frac{1}{2}} 
 \end{equation*}
$$ 

where $a_i$, $b_i$, $c_i$ and $d_i$ represent the number of events (death and no death) in a tocilizumab study $i$.

```{r}
W_fun = function(x) {
  sew = sqrt((1/(W*x$a + 1/2) + 1/(W*x$b + 1/2) + 1/(W*x$c + 1/2) + 1/(W*x$d + 1/2)))
  sew
}
```

```{r}
# Create data frame with only relevant data
toci_data = d_logOR %>% 
  filter(treatment == 0) %>% 
  mutate(a = trt_events,
         b = control_events,
         c = trt_total - trt_events,
         d = control_total - control_events) %>% 
  select(study, yi, sei, a:d) %>%
  as.data.frame()

# Vector of weights, ranging from 0.01 to 1

W = c(0.01, 0.05, seq(from = 0.1, to = 1, by = 0.1))

# Apply W_fun to create a data frame where each new column is the standard error
# per W
weight_data = plyr::adply(.data = toci_data, 
            .margins = 1, 
            .fun = function(x) W_fun(x)) %>% 
  
  # Select revelant columns
  select(study, yi, V1:last_col()) %>% 
  # Change new columns names
  setNames(c(colnames(toci_data)[1:2], paste0("seW_", W)))

```

Now, let's fit several frequentist random-effect meta-analysis (one per weight)

$$
\begin{align*}
y_i & \sim Normal(\theta_{i[W]}, \sigma_{i[W]}^2) \tag{Likelihood}\\
\theta_{i[W]} & \sim Normal(\mu_{tocilizumab[W]}, \tau_{[W]}^2)\\
\end{align*}
$$

```{r}

# Create vector with all standard error column names
column_names =
  colnames(weight_data) %>% 
  data.frame() %>% 
  rename(weights = ".") %>% 
  slice(3:n())

# Create empty list to fill below with all fits in the loop
tocilizumab_freq_models_w = list()

# Create empty data frame to fill with overall mean and sd from each fit per
# weight
dat = data.frame(weight = c(0.01, 0.05, seq(from = 0.1, to =  1, by = 0.1)),
                  mean = NA, sd = NA)

# Run loop to fit all 12 fits and save info in data frame and list
for (i in 1:nrow(column_names)) {
  
  # Pick a column name
  weight_value = column_names %>% slice(i) %>% pull()
  
  # Transform data object into the long format to be able to use filter() below
  d_w = 
    weight_data %>% 
  pivot_longer(seW_0.01:last_col(),
               names_to = "sei")
  
  # Filter only data regarding the weight_value above
  d_rma = 
    d_w %>% 
  filter(sei == weight_value)
  
  # Fit meta-analysis
  fit = rma(yi = yi, sei = value,
            data = d_rma,
            method = "REML", slab = study)
  
  # Save all fits in this list
  tocilizumab_freq_models_w[[i]] = fit
  
  # Save overall mean ($beta) and sd ($se) per model in this data frame
  dat[i, "mean"] = tocilizumab_freq_models_w[[i]]$beta
  dat[i, "sd"] = tocilizumab_freq_models_w[[i]]$se
  
}

## Change names of list indexing to facilitate data wrangling later
names(tocilizumab_freq_models_w) = dat$weight

## Save output
# saveRDS(tocilizumab_freq_models_w,
#         here("final_analyses/output/fits/main/frequentist_models_prior_fits.rds"))
# 
# saveRDS(dat,
#         here("final_analyses/output/fits/main/frequentist_models_prior_mean_sd.rds"))
```

## Sarilumab (likelihood) + Tocilizumab (prior) model

$$
\begin{align*}
y_i & \sim Normal(\theta_i, \sigma_i^2) \tag{Likelihood}\\
\theta_i & \sim Normal(\mu_{sarilumab[W]}, \tau^2)\\
\\
\mu_{sarilumab{[W]}} & = \mu_{tocilizumab[W]} \tag{Priors} \\
\tau & \sim \operatorname{Half-Normal}(0.5)
\end{align*}
$$


```{r, results="hide"}

# Same prior for tau in all models
tau_prior = prior_string("normal(0, 0.5)", class = "sd")

# Different priors for mu_sarilumab. 1 per W
# Define priors with string from arguments saved in dat (mean and sd)

# Weight = 0.01

## Create string to input it in prior_string() below
str_001 = paste0("normal(",
                 dat[1,2], # Mean
                 ",",
                 dat[1,3], # SD
                 ")")

## Create prior based on string above
mu_prior_001 = prior_string(str_001, class = "b", coef = "Intercept")

# Weight = 0.05
str_005 = paste0("normal(",dat[2,2],",",dat[2,3],")")
mu_prior_005 = prior_string(str_005, class = "b", coef = "Intercept")

# Weight = 0.10
str_010 = paste0("normal(",dat[3,2],",",dat[3,3],")")
mu_prior_010 = prior_string(str_010, class = "b", coef = "Intercept")

# Weight = 0.20
str_020 = paste0("normal(",dat[4,2],",",dat[4,3],")")
mu_prior_020 = prior_string(str_020, class = "b", coef = "Intercept")

# Weight = 0.30
str_030 = paste0("normal(",dat[5,2],",",dat[5,3],")")
mu_prior_030 = prior_string(str_030, class = "b", coef = "Intercept")

# Weight = 0.40
str_040 = paste0("normal(",dat[6,2],",",dat[6,3],")")
mu_prior_040 = prior_string(str_040, class = "b", coef = "Intercept")

# Weight = 0.50
str_050 = paste0("normal(",dat[7,2],",",dat[7,3],")")
mu_prior_050 = prior_string(str_050, class = "b", coef = "Intercept")

# Weight = 0.60
str_060 = paste0("normal(",dat[8,2],",",dat[8,3],")")
mu_prior_060 = prior_string(str_060, class = "b", coef = "Intercept")

# Weight = 0.70
str_070 = paste0("normal(",dat[9,2],",",dat[9,3],")")
mu_prior_070 = prior_string(str_070, class = "b", coef = "Intercept")

# Weight = 0.80
str_080 = paste0("normal(",dat[10,2],",",dat[10,3],")")
mu_prior_080 = prior_string(str_080, class = "b", coef = "Intercept")

# Weight = 0.90
str_090 = paste0("normal(",dat[11,2],",",dat[11,3],")")
mu_prior_090 = prior_string(str_090, class = "b", coef = "Intercept")

# Weight = 1
str_100 = paste0("normal(",dat[12,2],",",dat[12,3],")")
mu_prior_100 = prior_string(str_100, class = "b", coef = "Intercept")

# Put all priors together
priors = list(c(mu_prior_001, tau_prior), # W = 0.01
              c(mu_prior_005, tau_prior), # W = 0.05
              c(mu_prior_010, tau_prior), # W = 0.10
              c(mu_prior_020, tau_prior), # W = 0.20
              c(mu_prior_030, tau_prior), # W = 0.30
              c(mu_prior_040, tau_prior), # W = 0.40
              c(mu_prior_050, tau_prior), # W = 0.50
              c(mu_prior_060, tau_prior), # W = 0.60
              c(mu_prior_070, tau_prior), # W = 0.70
              c(mu_prior_080, tau_prior), # W = 0.80
              c(mu_prior_090, tau_prior), # W = 0.90
              c(mu_prior_100, tau_prior)) # W = 1.00
 
# Only data from sarilumab
sari_data = d_logOR %>% filter(treatment == 1)

# Define formula
mf = 
  formula(yi | se(sei) ~ 0 + Intercept + (1 | study))

# Define arguments for brm()
base_args = list(data = sari_data,
                 family = gaussian,
                 formula = mf,
                 iter = 4000, warmup = 2000, chains = 4,
                 cores = parallel::detectCores(),
                 control = list(adapt_delta = .99),
                 sample_prior = TRUE, seed = 123,
                 backend = "cmdstanr")

# Create vector with all weights to use later
vector_weights = data.frame(weight = c(0.01, 0.05, seq(from = 0.1, to =  1, by = 0.1)))

# Create list to store all fits
models_sarilumab_w = list()

## Run loop
# for (i in 1:nrow(vector_weights)) {
#   
#   # Show what model is running
#   print(vector_weights[i, c("weight")])
#   
#   # Put respective prior together with other arguments 
#   args = c(list(prior = priors[[i]]), base_args)
#   
#   # Fit model using brm()
#   fit = do.call(brm, args)
#   
#   # Store the whole model in a list, where
#   # [[1]] = 0.01 weight, [[2]] = 0.05, [[3]] = 0.10, [[4]] = 0.20, ...
#   # [[12]] = 1
#   models_sarilumab_w[[i]] = fit
# }

## Change names of list indexing to facilitate data wrangling later
# names(models_sarilumab_w) = vector_weights$weight

## Save list with all models
# saveRDS(models_sarilumab_w, 
#         here("final_analyses/output/fits/main/models_sarilumab_w.rds"))

# Load models
models_sarilumab_w = readRDS(
  here("final_analyses/output/fits/main/models_sarilumab_w.rds"))

```

### Priors

```{r, fig.align="center"}
vector_weights = data.frame(weight = c(0.01, 0.05, seq(from = 0.1, to =  1, by = 0.1)))

for (i in 1:nrow(column_names)) {
  
  lab = paste0("W = ", vector_weights %>% slice(i) %>% pull() )
  
  forest(tocilizumab_freq_models_w[[i]], transf = exp, xlab = "Odds Ratio")
  
  grid::grid.text(lab, .65, .7, gp=grid::gpar(cex=2))
  
}
```

These are the overall estimates from the frequentist models

```{r, fig.align="center"}

dat %>% 
  ggplot(aes(y = "", dist = distributional::dist_normal(mean, sd),
             color = sd)) +
  stat_dist_slab(fill = NA) +
  coord_cartesian(expand = FALSE) +
  labs(x = "log odds ratio", y = "Density\n") +
  theme_minimal()
```

```{r, fig.align="center"}
dat %>% 
  ggplot(aes(y = sd, dist = distributional::dist_normal(mean, sd))) +
  stat_dist_halfeye(position = "dodge",
                    .width = .95) +
  labs(x = "log odds ratio", y = "Standard deviation of each distribution\n") +
  theme_minimal()
```


### Diagnostics plots

##### Sarilumab + Tocilizumab model

```{r, fig.align='center'}
# Run loop
for (i in 1:nrow(vector_weights)) {
  # Run custom function diag_plot, 1 per weight
p = diag_plot(model = models_sarilumab_w[[i]],
          pars_list = c("b_Intercept", "sd_study__Intercept"),
          ncol_trace = 4)
# Display plot
print(p)  

# Add legend to show respective weight
lab = paste0("W = ", vector_weights %>% slice(i) %>% pull() )
grid::grid.text(lab, .75, .05, gp=grid::gpar(cex=2))
}
```

Posterior predictive check

```{r, fig.align='center'}
# Run lopp
for (i in 1:nrow(vector_weights)) {
p = pp_check(models_sarilumab_w[[i]], nsamples = 50)

print(p)

lab = paste0("W = ", vector_weights %>% slice(i) %>% pull() )
grid::grid.text(lab, .8, .9, gp=grid::gpar(cex=2))
}
```


```{r}
sessionInfo()
```

